---
title: "Simple document"
output:  github_document

---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`. 

**Write a named code chunk that creates a dataframe comprised of:** 
**1) a numeric variable containing a random sample of size 500**
**2) from a normal variable with mean 1**
**3) a logical vector indicating whether each sampled value is greater than 0** **4) and a numeric vector containing the absolute value of each element** 
**Then** 
**produce a histogram of the absolute value variable just created** 
**Add an inline summary giving the median value rounded to two decimal places**
**What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?**

```{r learning assesment_1} 
library(tidyverse) 
la_df = tibble(
  norm_samp = rnorm(500, mean = 1), 
  norm_samp_pos = norm_samp > 0, 
  abs_norm_samp = abs(norm_samp)
)

ggplot(la_df, aes(x =abs_norm_samp)) + geom_histogram()

median_samp = median(pull(la_df, norm_samp))
```
The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.

# Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell


